PANCHANGE_analysis

### 2020-08-19 PANCHANGE_analysis.Rmd
first crude regression models

Load packages
```{r Load packages}
library(knitr)
library(summarytools)
library(psych)
library(eeptools) # Needed to calculate age from birthdate
library(tidyverse)
```

@@

@@

Model 0: Disorders
```{r}

Model 1: Model 0 + Sex + Age + Ethnicity + Time registration and baseline
```{r}

>>>>

Load packages
```{r Load packages}
library(knitr)
library(summarytools)
library(psych)
library(patchwork)
library(broom)
library(tidyverse)
```

@@

```{r}
gad.diff_score_prepan_base_plot <- dat %>%
  ggplot(mapping = aes(y = gad.diff_score_prepan_base)) +
  geom_bar() +
  theme_minimal()

gad.diff_score_prepan_retro_plot <- dat %>%
  ggplot(mapping = aes(y = gad.diff_score_prepan_retro)) +
  geom_bar() +
  theme_minimal()

gad.diff_score_prepan_base_plot <- dat %>%
  ggplot(mapping = aes(y = gad.diff_score_prepan_base)) +
  geom_bar() +
  theme_minimal()

```{r fig.height=5, fig.width=5}
gad.diff_score_prepan_base_plot /
  gad.diff_score_prepan_retro_plot /
  gad.diff_score_prepan_base_plot +
  plot_layout(guides = "collect", heights = c(1,1,1)) +
  plot_annotation(tag_levels = "A")
```

@@

Model 0: Disorders
```{r}
model0 <- lm(
  formula = gad.diff_score_base_retro ~ Disorder,
  data = dat.long)

summary(model0)
```

```{r}
tidy(model0)
```

```{r}
model1 <- lm(
  formula = gad.diff_score_base_retro ~ time_diff_sign_up_coping,
  data = dat)

summary(model1)
```

Model 1: Model 0 + Sex + Age + Ethnicity + Time registration and baseline
```{r}
model1 <- lm(
  formula = gad.diff_score_base_retro ~ Gender + Age + Ethnicity + time_diff_sign_up_coping + Sample,
  data = dat)

summary(model1)
```
